---
title: "Practical 2"
author: "Jumping Rivers"
output:
  tufte::tufte_handout:
    latex_engine: xelatex
  tufte::tufte_html: default
vignette: >
  %\VignetteIndexEntry{practical2}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo=FALSE, message=FALSE}
library("jrAutomate")
library("flexdashboard")
```

For links to any webpages, see `vignette("links", package = "jrAutomate")`

## Exercise 1 (5 minutes)

  * Briefly explore the [showcase](http://www.htmlwidgets.org/showcase_leaflet.html)^[See `vignette("links", package = "jrAutomate")`] htmlwidgets. 

## Exercise 2 (20 minutes)

Go through the following widgets. See `vignette("links", package = "jrAutomate")` for the links to each bullet point.

  * Interactive Heat Maps: [d3heatmap](d3heatmap.html), [R](d3heatmap.R), [Rmd](d3heatmap.Rmd)
  * Interactive tables: [DT](DT.html), [R](DT.R), [Rmd](DT.Rmd)
  * Circle Plots with Bundled Edges: [edgebundleR](edgebundleR.html), [R](edgebundleR.R), [Rmd](edgebundleR.Rmd)
  * Formattable Data Structures: [formattable](formattable.html), [R](formattable.R), [Rmd](formattable.Rmd)
  * Interactive ggplot2 graphs: [ggiraph](ggiraph.html), [R](ggiraph.R), [Rmd](ggiraph.Rmd)
  * Network graphs: [networkD3](networkD3.html), [R](networkD3.R), [Rmd](networkD3.Rmd)
  * Add pan and zoom to graphics: [svgPanZoom](svgPanZoom.html), [R](svgPanZoom.R), [Rmd](svgPanZoom.Rmd)
  * jQuery Sparkline HTML Widget: [sparkline](sparkline.html), [R](sparkline.R), [Rmd](sparkline.Rmd)

Experiment with a few of the widgets on your **own** data set.

## Exercise 3 (20 minutes)

Open the `htmlwidgets` vignette

```{r eval=FALSE}
vignette("htmlwidgets", package="jrAutomate")
```

Explore the **other widgets** on you own data. The `plotly` framework, under _Entire plotting frameworks_ is quite nice

## Exercise 4 (10 minutes)

Create:

  * A markdown document containing your widgets;
  * A markdown presentation containing your widgets.
  
  
  
