---
title: "Practical 1"
author: "Jumping Rivers"
output:
  tufte::tufte_handout:
    latex_engine: xelatex
  tufte::tufte_html: default
vignette: >
  %\VignetteIndexEntry{practical1}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
  
```{r echo=FALSE, message=FALSE}
library("jrAutomate")
```

For links to any webpages, see `vignette("links", package = "jrAutomate")`

## Exercise 1 (8 minutes)

  * In RStudio, select `File`, then `New Project`. Create a new RStudio project in 
  an empty directory.
  * Run the command `jrAutomate::create_project()`. This should create two directories: `original`
  and `exercises`.
  * Open `exercises/chapter1/rmarkdown1.Rmd`. Click `Knit HTML`
  * Complete the instructions in the file

## Exercise 2 (8 minutes)

  * Open `exercises/chapter1/rmarkdown2.Rmd`. Click `Knit HTML`
  * Complete the instructions in the file
  
## Exercise 3 (15 minutes)

  * Open `exercises/chapter1/rmarkdown3.Rmd`. Click `Knit HTML`
  * We can change how the slides are displayed:
    * Swap `output: ioslides_presentation` to `output:slidy_presentation` to re-knit
    * Install the `reveal.js` package
        ```{r eval=FALSE}
        install.packages("revealjs")
        ```
    and change te output format to `output: revealjs::revealjs_presentation`. On my machine, I had to view the
    presentation in a browser on full-screen mode. More details are available at 
    the Rstudio web-page^[`vignette("links", package = "jrAutomate")`].
  * Change the slides to use your data.
  
  
