---
title: "Practical 3"
author: "Jumping Rivers"
output:
  tufte::tufte_handout:
    latex_engine: xelatex
  tufte::tufte_html: default
vignette: >
  %\VignetteIndexEntry{practical3}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  ---
  
```{r echo=FALSE, message=FALSE}
  library("jrAutomate")
  library("flexdashboard")
```
  
For links to any webpages, see `vignette("links", package = "jrAutomate")`
  
## Exercise 1 (15 minutes)
  
1. Open `exercises/chapter3/single_column_fill.Rmd` and Knit. 
  * Add two additional charts to get the following layout
  
```{r echo=FALSE, fig.height=2, fig.width=2}
  layout(matrix(c(1:4), 4, 1, byrow = TRUE))
  layout_show(4, 2)
```

2. What is the difference between `Column (fill)` and `Column (scroll)`. 
  Hint: create a dashboard with $6$ charts for `fill` and `scroll`
  
3. Open `exercises/chapter3/row.Rmd`. Recreate the following layouts
  
*  Layout 1
  
```{r echo=FALSE, fig.height=2, fig.width=2}
layout(matrix(c(1:4), 2, 2, byrow = TRUE))
layout_show(4, 1)
```

*  Layout 2

```{r echo=FALSE, fig.height=2, fig.width=2}
layout(matrix(c(1:2, 3, 3, 4:5), 3, 2, byrow = TRUE))
layout_show(5, 1)
```

## Exercise 2 (15 minutes)

Create the following layouts

* Layout 1 (use `{data-width=XXX}`)

```{r echo = FALSE, fig.height = 2, fig.width = 2}
layout(matrix(c(1, 1, 2, 3:5), 2, 3, byrow = TRUE))
layout_show(5, 1)
```

* Layout 2 (use `{data-height=XXX}`)

```{r echo = FALSE, fig.height = 2, fig.width = 2}
layout(matrix(c(1, 1, 2, 1, 1, 2, 3:5), 3, 3, byrow = TRUE))
layout_show(5, 1)
```

## Exercise 3 (30 minutes)

1. Open the `Multiple columns` `.Rmd` file and knit. 
Create the following layout.

```{r echo=FALSE, fig.height=2, fig.width=2}
layout(matrix(c(1, 1, 2, 4,
                1, 1, 2, 5,
                1, 1, 3, 6,
                1, 1, 3, 7), 4, 4, byrow = TRUE))
layout_show(7, 1)
```

2. Open `chapter3/pages.Rmd`. 
* Open the vignette `components`

```{r eval=FALSE}
vignette("components", package = "jrAutomate")
```

to give you an idea of what is possible. The source code for the vignette is in the file
`chapter3/components.Rmd`

*  Create a dashboard with $3$ pages. Add some graphs (perhaps using htmlwidgets) of your own data.

3. The flexdashboard^[See `vignette("links", package = "jrAutomate")`] [documentation](http://rmarkdown.rstudio.com/flexdashboard/using.html#multiple_pages)
gives more details on pages. Including, 
* [Orientation](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_orientation)
* [Navigation](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_navigation)
* [Links](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_links) and [icons](http://rmarkdown.rstudio.com/flexdashboard/using.html#page_icons)

## Exercise 4 (20 minutes)

1. It's easy to create tab panes. 

* Open `chapter3/tabs.Rmd`. 
* What does the `.tabset-fade` attribute do?
* Alter one of your existing layouts and add a tab component

2. Another neat layout is [Storyboard](http://rmarkdown.rstudio.com/flexdashboard/using.html#storyboards)^[See `vignette("links", package = "jrAutomate")`]

* Knit `chapter3/story.Rmd`.
* Add an additional frame to the storyboard containing a `boxplot` of the simulated data.
* [Example](https://beta.rstudioconnect.com/jjallaire/htmlwidgets-showcase-storyboard/)^[See `vignette("links", package = "jrAutomate")`] from RStudio


