---
title: "Chapter 2: htmlwidgets"
author: Colin Gillespie
date: "`r Sys.Date()`"
#output: revealjs::revealjs_presentation
output: ioslides_presentation
css: left.css
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Chapter 2 Slides}
-->

## htmlwidgets


```{r echo=FALSE, message=FALSE}
# initiate a 100 x 3 matrix filled with zeros
m <- matrix(numeric(300), ncol = 3)
# simulate a 3D random-walk
for (i in 2:100) m[i, ] <- m[i-1, ] + rnorm(3)
# collect everything in a data-frame
df <- setNames(
  data.frame(m, seq(1, 100)),
  c("x", "y", "z", "time")
)
library(plotly)
plot_ly(data=df, x = ~x, y = ~y, z = ~z, color = ~time, type = "scatter3d")
```

## htmlwidgets
```{r echo=FALSE}
library(plotly)
data("diamonds", package="ggplot2")
d <- diamonds[sample(nrow(diamonds), 500), ]
d$clarity = paste("Clarity:", d$clarity)
plot_ly(d, x = ~carat, y = ~price, text = ~clarity,
        mode = "markers", color = ~carat, size = ~carat)
```

## htmlwidgets

  * Used just like conventional R plots;
  * Included in R Markdown documents;
  * Incorporated into shiny web applications.

## htmlwidgets

Using an existing R html widgets requires very little code. 

# Exercise 1
## Exercise 1
```{r eval=FALSE}
vignette("chapter2", package="jrShiny")
```

# Creating widgets
## Creating widgets

  * Creating widgets is also straightforward
  * In fact someone created a new widget every week for a [year](http://www.buildingwidgets.com/)
  * New HTML widgets are being released all the time
  * The course package provides an up-to-date overview of the currently available widgets

# Exercise 2
## Exercise 2
```{r eval=FALSE}
vignette("chapter2", package="jrShiny")
```









