---
title: "Twitter"
author: "Jumping Rivers"
output: html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Twitter}
-->

## Accessing twitter from the command line

An easy way of determining when your job/script has finished, is to use [twitter](https://twitter.com/csgillespie);
at the end of your job, you send a tweet!

The package for accessing the twitter API is [rtweet](https://github.com/mkearney/rtweet).
This replaces the older **twitteR** client. 

1. Install the package - `install.packages("rtweet")`
1. In order to programmatically access twitter, you need to set up an app. This
is described in great detail in the [vignette](https://mkearney.github.io/rtweet/articles/auth.html)

1. Next you create a token:

    ```{r eval=FALSE}
    library(rtweet)
    ## name assigned to created app
    appname <- "rtweet_token"
    ## api key (example below is not a real key)
    key <- "XYznzPFOFZR2a39FwWKN1Jp41"
    ## api secret (example below is not a real key)
    secret <- "CtkGEWmSevZqJuKl6HHrBxbCybxI1xGLqrD5ynPd9jG0SoHZbD"
    twitter_token <- create_token(
      app = appname,
      consumer_key = key,
      consumer_secret = secret)
    ```

1. Once `twitter_token` is part of your global environment, rtweet functions should find it. However, using this method, the token will not automatically load in future sessions (you'll need to create a token every time you start a new session).

    ```{r eval=FALSE}
    ## Search for tweets
    rt = search_tweets("#rstats", n = 1000, token = twitter_token)
    ## Follows a user
    post_follow("csgillespie")
    ```

  
